Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2014-10-09 Report/joint_wsrm_formulation.tex
modified with markku input

The \ac{Q-WSRM} formulation extends the \emph{backpressure algorithm} to the downlink \ac{MIMO}-\ac{OFDM} framework, in which the multiple \acp{BS} act as the source nodes and the user terminals as the receiver nodes. The control policy in the form of transmit precoders aims at minimizing the number of queued packets waiting in the \acp{BS}. In order to find the optimal strategy, we resort to the Lyapunov theory, which is predominantly used in the control theory to achieve system stability. Since at each time slot, the system is described by the channel conditions and the number of backlogged packets of each user, the Lyapunov function is used to provide a scalar measure, which grows large when the system moves toward the undesirable state. Following similar approach as in \cite{neely2010stochastic}, the scalar measure for the queue stability is given by
\begin{equation}
\mathrm{L}\sset{\mbf{Q}(i)} = \frac{1}{2} \, \sum_{k \in \mc{U}} Q_k^2(i),
\end{equation}
where \me{\mbf{Q}(i)} denotes the stacked user queues at the \me{\ith{i}} slot and \me{\tfrac{1}{2}} is used for the convenience. It provides a scalar measure of congestion present in the system \cite[Ch. 3]{neely2010stochastic}.

@@

Now, the conditional Lyapunov drift, denoted by \me{\Delta{(\mbfa{Q}(i))}}, is given by the infimum over the transmission rate as
\iftoggle{single_column}{
\begin{IEEEeqnarray}{rCl} \label{backpressure-approx}
	\underset{\mbf{t}}{\text{inf}} &\quad& \Delta(\mbf{Q}(i)) \triangleq \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
	&\leq& \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)}}_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)}, \eqsub \label{backpressure-approx-1b}
\end{IEEEeqnarray}}{
\begin{IEEEeqnarray}{CL} \label{backpressure-approx}
	\underset{\mbf{t}}{\text{inf}} \quad & \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
	\leq & \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \Big \lbrace \sum_{k \in \mc{U}} \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i) \Big \rbrace }_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) \nonumber \\
	& \qquad \qquad {} - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\Big \lbrace \sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i) \Big \rbrace, \eqsub \label{backpressure-approx-1b}
\end{IEEEeqnarray}}
where the subscripts \me{\mbf{t}} and \me{\mbfa{\lambda}} represents the vector obtained by stacking the transmission and the arrival rate of all users present in the system. Since the transmission and the arrival rates are bounded, we can upper bound the second order moments in the first term of \eqref{backpressure-approx-1b} by a constant \me{B} in order to  eliminated from the optimization problem \cite{neely2010stochastic}. The second term in \eqref{backpressure-approx-1b} follows from the Poisson arrival process.

@@

In order to avoid the excessive  allocation of the resources, we include an additional rate constraint \me{t_k \leq Q_k} to address \me{[x]^+} operation in \eqref{eqn-2a}. The rate constrained version of the \ac{Q-WSRM}, denoted by \ac{Q-WSRME} problem for a cellular system, is given by \label{q_gen_sum-1} with the additional constraint
\begin{IEEEeqnarray}{rCl} \label{eqn-3.1.4}
\sum_{n=1}^N \sum_{l = 1}^L \log_2(1 + \gamma_{l,k,n}) \leq Q_k, \fall k \in \mc{U},
\end{IEEEeqnarray}
where the precoders are associated with the \me{\gamma_{l,k,n}} defined in \eqref{eq:SINR}. By using the number of queued packets as the weights, the resources can be allocated to the user with the more number of backlogged packets, which essentially does the allocation in a greedy manner.

As a special case of the problem defined in \eqref{q_gen_sum}, we can formulate the sum rate maximization problem by setting the weights in \eqref{eqn-3.1.1} as unity, leading to the problem as in \eqref{q_gen_sum} with \me{Q_k = 1, \forall k \in \mc{U}}. This approach provides a greedy queue minimizing allocation as compared to \ac{Q-WSRME}, since the resource allocation is driven by the channel conditions in comparison with the number of queued packets as in \ac{Q-WSRME}. Note that in both formulations, the resources allocated to the users are limited by the backlogged packets with an explicit maximum rate constraint defined by \eqref{eqn-3.1.4}.

>>>>

The \ac{Q-WSRM} formulation extends the \emph{backpressure algorithm} to the downlink \ac{MIMO}-\ac{OFDM} framework, in which the multiple \acp{BS} act as the source nodes and the user terminals as the receiver nodes. The control policy in the form of transmit precoders aims at minimizing the number of queued packets waiting in the \acp{BS}. In order to find the optimal strategy, we resort to the Lyapunov theory, which is predominantly used in the control theory to achieve system stability. Since at each time slot, the system is described by the channel conditions and the number of backlogged packets of each user, the Lyapunov function is used to provide a scalar measure, which grows large when the system moves toward the undesirable state. Following similar approach as in \cite{neely2010stochastic}, the scalar measure for the queue stability is given by
\begin{equation}
\mathrm{L}\sset{\mbf{Q}(i)} = \frac{1}{2} \, \sum_{k \in \mc{U}} Q_k^2(i),
\end{equation}
where \me{\mbf{Q}(i) = \sset{Q_1(i),Q_2(i),\dotsc,Q_K(i)}^\mathrm{T}} and \me{\tfrac{1}{2}} is used for the convenience. It provides a scalar measure of congestion present in the system \cite[Ch. 3]{neely2010stochastic}.

@@

Now, the conditional Lyapunov drift, denoted by \me{\Delta{(\mbfa{Q}(i))}}, is given by the infimum over the transmission rate as
\iftoggle{single_column}{
\begin{IEEEeqnarray}{rCl} \label{backpressure-approx}
	\underset{\mbf{t}}{\text{inf}} &\quad& \Delta(\mbf{Q}(i)) \triangleq \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
	&\leq& \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)}}_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)}, \eqsub \label{backpressure-approx-1b}
\end{IEEEeqnarray}}{
\begin{IEEEeqnarray}{CL} \label{backpressure-approx}
	\underset{\mbf{t}}{\text{inf}} \quad & \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
	\leq & \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \Big \lbrace \sum_{k \in \mc{U}} \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i) \Big \rbrace }_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) \nonumber \\
	& \qquad \qquad {} - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\Big \lbrace \sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i) \Big \rbrace, \eqsub \label{backpressure-approx-1b}
\end{IEEEeqnarray}}
where the subscripts \me{\mbf{t}} and \me{\mbfa{\lambda}} represents the vector formed by stacking the transmission and the arrival rate of all users in the system. Since the transmission and the arrival rates are bounded, the second order moments in the first term of \eqref{backpressure-approx-1b} can be bounded by a constant \me{B} without affecting the optimal solution of the problem \cite{neely2010stochastic}. The second term in \eqref{backpressure-approx-1b} follows from the Poisson arrival process.

@@

In order to avoid the excessive  allocation of the resources, we include an additional rate constraint \me{t_k \leq Q_k} to address \me{[x]^+} operation in \eqref{eqn-2a}. The rate constrained version of the \ac{Q-WSRM}, denoted by \ac{Q-WSRME} problem for a cellular system, is given by \label{q_gen_sum-1} with the additional constraint
\begin{IEEEeqnarray}{rCl} \label{eqn-3.1.4}
\sum_{n=1}^N \sum_{l = 1}^L \log_2(1 + \gamma_{l,k,n}) \leq Q_k, \fall k \in \mc{U},
\end{IEEEeqnarray}
where the precoders are associated with \me{\gamma_{l,k,n}} defined in \eqref{eq:SINR}. By using the number of queued packets as the weights, the resources can be allocated to the user with the more backlogged packets, which essentially does the allocation in a greedy manner.

As a special case of the problem defined in \eqref{q_gen_sum}, we can formulate the sum rate maximization problem by setting the weights in \eqref{eqn-3.1.1} as unity, leading to the problem as in \eqref{q_gen_sum} with \me{Q_k = 1, \forall k \in \mc{U}}. This approach provides a greedy queue minimizing allocation as compared to \ac{Q-WSRME}, since the resource allocation is driven by the channel conditions in comparison to the number of queued packets as in \ac{Q-WSRME}. Note that in both formulations, the resources allocated to the users are limited by the number of backlogged packets with an explicit maximum rate constraint defined by \eqref{eqn-3.1.4}.

### 2014-10-09 Report/kkt_mse_approach.tex
cooker-night
modified with markku input

The distributed solutions via primal and \ac{ADMM} approaches depend on the subgradient update by using a step size parameter for the coupling variables, which affects the speed of convergence to the optimal value. In this method, we provide an alternative approach to decentralize the \ac{MSE} equivalent problem considered in \cite{christensen2008weighted,wmmse_shi} by directly solving the \ac{KKT} conditions. Similar work has been considered for the \ac{WSRM} problem with the minimum rate constraints in \cite{kaleva2013decentralized,kaleva2013primal}. When the queues are involved, the maximum rate constraint imposed by the number of queued packets at the \ac{BS} includes a nonconvex constraint, which makes the problem difficult to solve due to the additional nonconvex maximum rate constraint \eqref{eqn-3.1.4} for the \ac{WSRM} problem.

Even though the rate constraints are implicitly present in the objective function, we cannot formulate the \ac{KKT} conditions readily due to the non-differentiable objective function. The non-differentiability of the objective function is due to the absolute operator present in the norm function. In order to make the objective function differentiable, we consider the following case for which the absolute operator can be ignored without affecting the optimal solution, namely,
\begin{itemize}
\item when the exponent \me{q} is even or,
\item when the number of backlogged packets of each user is large enough, \textit{i.e}, \me{Q_k \gg \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}} to ignore the absolute operator and the queues as well.
\end{itemize}

With the assumption of either one of the above conditions to be true, the problem in \eqref{eqn-mse-2} can be written as
\iftoggle{single_column}{
\begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \\ \epsilon_{l,k,n}, \mvec{W}{k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
\text{subject to} & \hspace{0.5cm} & \nonumber \\
\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \, \|\mvec{w}{l,k,n}\|^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
\sigma_{l,k,n} : & \hspace{0.5cm} & \log(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
\end{IEEEeqnarray}
}{
\begin{IEEEeqnarray}{Rl}\label{kkt-mse-1}
	\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \\ \epsilon_{l,k,n}, \mvec{W}{k,n}}}{\text{minimize}} & \quad \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
	\text{subject to} & \nonumber \\
	\alpha_{l,k,n} : &  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \|\mvec{w}{l,k,n}\|^2 \nonumber \\
	& + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
	\sigma_{l,k,n} : &  \log_2(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2)\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.3} \\
	\delta_b : & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \eqspace \label{kkt-mse-1.4}
\end{IEEEeqnarray}
}
where \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b} are the dual variables corresponding to the constraints defined in \eqref{kkt-mse-1.2}, \eqref{kkt-mse-1.3} and \eqref{kkt-mse-1.4}.

@@

Since the dual variables \me{\alpha^{(i)}} and \me{\sigma^{(i)}} are interdependent in \eqref{kkt-mse-4}, one has to be fixed to optimize for the other. In this problem, we fix the dual variable \me{\alpha^{(i)}} to a fixed value as in \eqref{kkt-mse-4.1} to obtain the other variables in \eqref{kkt-mse-4}. At each iteration, the dual variable \me{\alpha^{(i)}} is updated linearly from the earlier value \me{\alpha^{(i-1)}} by a step size of \me{\rho \in [0,1]}. It can be seen that, when the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be negative thereby forcing the dual variable \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}}, which in turn reduce the transmit precoder weights in \eqref{kkt-mse-4.3}. This reduction in the precoder weights forces the allocated rate of the user \me{k} to reduce from the previous iteration as \me{t_k^{(i)} < t_k^{(i-1)}}.

The \ac{KKT} solutions provided in \eqref{kkt-mse-4} are solved in an iterative manner by initializing the transmit and the receive precoders \me{\mvec{M}{k,n},\mvec{W}{k,n}} with the single user beamforming and the \ac{MMSE} vectors. The dual variable \me{\alpha}'s corresponding to precoder weights are initialized with ones to provide equal priorities to all streams. Now, the closed form expressions in \eqref{kkt-mse-4} are evaluated sequentially until convergence or to a certain accuracy. In \eqref{kkt-mse-4}, all expressions are in closed form except the transmit precoders \eqref{kkt-mse-4.3}, which depends on the \ac{BS} specific dual variable \me{\delta_b}. It can be solved efficiently by the bisection method satisfying the power constraint \eqref{kkt-mse-1.4}. After each iteration instant, the transmit and the receive precoders are updated across the coordinating \acp{BS} in \me{\mc{B}} to obtain the next operating point.

In order to perform the distributed approach, we can consider the method proposed in \cite{komulainen2013effective}, where the users evaluate the \ac{MSE}, and the dual variable \me{\alpha_{l,k,n}} using the transmission made by all \acp{BS} using the updated transmit precoders \me{\mvec{m}{l,k,n}^{(i-1)}}. Once the dual variables are evaluated, the users will notify the dual variables and the receive beamformers to the \acp{BS} using uplink precoded pilots, where the uplink precoder is given by \me{\mvec{\tilde{w}}{l,k,n}^{(i-1)} = \sqrt{\alpha_{l,k,n}^{(i-1)}}\mvec{w}{l,k,n}^{\ast(i-1)}}. Upon receiving the uplink precoded pilots at the \ac{BS} \me{b}, the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{\tilde{w}}{l,k,n}^{(i-1)}} can be measured and used in the expression \eqref{kkt-mse-4.3} to update the transmit precoders, where \me{\mbf{x}^{\ast}} represents the conjugate of \me{\mbf{x}}. The algorithmic representation of the distributed \ac{MSE}-\ac{KKT} scheme is shown in the Algorithm. \ref{algo-4}.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=1}, \me{\mbf{w}^{(0)}_{l,k,n},\epsilon_{l,k,n}^{(0)}} randomly, dual variables \me{{\alpha}_{l,k,n}^{(0)} = 1}, and \me{I_{\max}}}
 \ForEach{\ac{BS} \me{b \in \mc{B}}}{
 initialize \me{i = 0} \;
 \Repeat{until convergence or \me{i \geq I_{\max}}}{
	find \me{\mvec{M}{k,n}^{(i)}} using \eqref{kkt-mse-4.3}, where \me{\delta_b} is obtained by bisection search satisfying \eqref{kkt-mse-1.4} \;
	update \me{\epsilon_{l,k,n}^{(i)}}, \me{t_{l,k,n}^{(i)}}, \me{\sigma_{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1} at \ac{BS} \me{b} and perform precoded downlink pilot transmission with \me{\mvec{M}{k,n}^{(i)}}\;
	update \me{\mvec{W}{k,n}^{(i+1)}} using \eqref{kkt-mse-4.6} and notify to all \acp{BS} using uplink precoded pilot with \me{\mvec{\tilde{w}}{l,k,n}^{(i+1)}} as the precoder\;
	\me{i = i + 1} \;
 }
 }
 \caption{\ac{KKT} approach for the \ac{JSFRA} scheme}
 \label{algo-4}
\end{algorithm}

>>>>

The distributed solutions via primal and \ac{ADMM} approaches depend on the subgradient update by using a step size parameter for the coupling variables. It affects the speed of convergence to the optimal value. In this method, we provide an alternative approach to decentralize the \ac{MSE} equivalent problem considered in \cite{christensen2008weighted,wmmse_shi} by directly solving the \ac{KKT} conditions. Similar work has been considered for the \ac{WSRM} problem with the minimum rate constraints in \cite{kaleva2013decentralized,kaleva2013primal}. When the queues are involved, the maximum rate constraint imposed by the number of queued packets at the \ac{BS} includes a nonconvex constraint, which makes the problem difficult to solve due to the additional nonconvex maximum rate constraint \eqref{eqn-3.1.4} for the \ac{WSRM} problem.

Even though the rate constraints are implicitly present in the objective function, we cannot formulate the \ac{KKT} conditions readily due to the non-differentiable objective function. The non-differentiability is due to the absolute operator present in the norm function. In order to make the objective function differentiable, we consider the following case for which the absolute operator can be ignored without affecting the optimal solution, namely,
\begin{itemize}
\item when the exponent \me{q} is even, or
\item when the number of backlogged packets of each user is large enough, \textit{i.e}, \me{Q_k \gg \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}} to ignore the absolute operator, which means also ignoring the queues in the first place as well.
\end{itemize}

With the assumption of either one of the above conditions to be true, the problem in \eqref{eqn-mse-2} can be written as
\iftoggle{single_column}{\allowdisplaybreaks
\begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \\ \epsilon_{l,k,n}, \mvec{W}{k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
\text{subject to} & \hspace{0.5cm} & \nonumber \\
\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \, \|\mvec{w}{l,k,n}\|^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \eqspace \IEEEyessubnumber \label{kkt-mse-1.2} \\
\sigma_{l,k,n} : & \hspace{0.5cm} & \log(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
\end{IEEEeqnarray}
}{
\begin{IEEEeqnarray}{Rl}\label{kkt-mse-1}
	\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \\ \epsilon_{l,k,n}, \mvec{W}{k,n}}}{\text{minimize}} & \quad \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
	\text{subject to} & \nonumber \\
	\alpha_{l,k,n} : &  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \|\mvec{w}{l,k,n}\|^2 \nonumber \\
	& + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
	\sigma_{l,k,n} : &  \log_2(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2)\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.3} \\
	\delta_b : & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \eqspace \label{kkt-mse-1.4}
\end{IEEEeqnarray}
}
where \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b} are the dual variables corresponding to the constraints defined in \eqref{kkt-mse-1.2}, \eqref{kkt-mse-1.3} and \eqref{kkt-mse-1.4}.

@@

Since the dual variables \me{\alpha^{(i)}} and \me{\sigma^{(i)}} are interdependent in \eqref{kkt-mse-4}, one has to be fixed to optimize for the other. In this problem, we fix the dual variable \me{\alpha^{(i)}} to a fixed value as in \eqref{kkt-mse-4.1} to obtain the other variables in \eqref{kkt-mse-4}. At each iteration, the dual variable \me{\alpha^{(i)}} is updated linearly from the earlier value \me{\alpha^{(i-1)}} by a step size of \me{\rho \in [0,1]}. It can be seen that, when the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be negative thereby forcing the dual variable \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}}, which in turn reduces the transmit precoder weights in \eqref{kkt-mse-4.3}. This reduction in the precoder weights forces the allocated rate of user \me{k} to reduce from the previous iteration as \me{t_k^{(i)} < t_k^{(i-1)}}.

The \ac{KKT} solutions provided in \eqref{kkt-mse-4} are solved in an iterative manner by initializing the transmit and the receive precoders \me{\mvec{M}{k,n},\mvec{W}{k,n}} with the single user beamforming and the \ac{MMSE} vectors. The dual variable \me{\alpha}'s corresponding to precoder weights are initialized with ones to provide equal priorities to all streams. Now, the closed form expressions in \eqref{kkt-mse-4} are evaluated sequentially until convergence or to a certain accuracy. In \eqref{kkt-mse-4}, all expressions are in a closed form except the transmit precoders \eqref{kkt-mse-4.3}, which depend on the \ac{BS} specific dual variable \me{\delta_b}. It can be solved efficiently by the bisection method satisfying the power constraint \eqref{kkt-mse-1.4}. After each iteration instant, the transmit and the receive precoders are updated across the coordinating \acp{BS} in \me{\mc{B}} to obtain the next operating point.

In order to find the distributed solution, we can consider the method proposed in \cite{komulainen2013effective}, where the users evaluate the \ac{MSE} and the dual variable \me{\alpha_{l,k,n}} using the transmission made by all \acp{BS} and the updated transmit precoders \me{\mvec{m}{l,k,n}^{(i-1)}}. Once the dual variables are evaluated, the users will notify the dual variables and the receive beamformers to the \acp{BS} using the uplink precoded pilots, where the uplink precoder is \me{\mvec{\tilde{w}}{l,k,n}^{(i-1)} = \sqrt{\alpha_{l,k,n}^{(i-1)}}\mvec{w}{l,k,n}^{\ast(i-1)}}. Upon receiving the uplink precoded pilots at the \ac{BS} \me{b}, the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{\tilde{w}}{l,k,n}^{(i-1)}} can be measured and used in the expression \eqref{kkt-mse-4.3} to update the transmit precoders, where \me{\mbf{x}^{\ast}} represents the conjugate of \me{\mbf{x}}. The algorithmic representation of the distributed \ac{MSE}-\ac{KKT} scheme is shown in the Algorithm. \ref{algo-4}.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=1}, \me{\mbf{w}^{(0)}_{l,k,n},\epsilon_{l,k,n}^{(0)}} randomly, dual variables \me{{\alpha}_{l,k,n}^{(0)} = 1}, and \me{I_{\max}}}
 \ForEach{\ac{BS} \me{b \in \mc{B}}}{
 initialize \me{i = 0} \;
 \Repeat{until convergence or \me{i \geq I_{\max}}}{
	find \me{\mvec{M}{k,n}^{(i)}} using \eqref{kkt-mse-4.3}, where \me{\delta_b} is obtained by bisection search satisfying \eqref{kkt-mse-1.4} \;
	update \me{\epsilon_{l,k,n}^{(i)}}, \me{t_{l,k,n}^{(i)}}, \me{\sigma_{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1} at \ac{BS} \me{b} and perform precoded downlink pilot transmission with \me{\mvec{M}{k,n}^{(i)}}\;
	update \me{\mvec{W}{k,n}^{(i+1)}} using \eqref{kkt-mse-4.6} and notify to all \acp{BS} using uplink precoded pilot with \me{\mvec{\tilde{w}}{l,k,n}^{(i+1)}} as the precoder\;
	\me{i = i + 1} \;
 }
 }
 \caption{\ac{KKT} approach for the \ac{JSFRA} scheme}
 \label{algo-4}
\end{algorithm}
